Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
with subtables, maybe not worth the space

\usepackage{code}
\usepackage{graphicx}
\usepackage{balance}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{listings}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{url}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{xspace}

@@

% ---------------- C++ table UM Only--------------------------
\begin{table}[hbtp]
\centering
\caption{C++ (Regex vs. Comby)}
\label{tab:table_cpp1}
\begin{tabular}{l|r|cr|cr}
\toprule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
ompl & 525 & $\frac{595}{2533}$ & 23.49\% &  $\frac{564}{2127}$  & 25.94\%   \\[1ex]
libgraphqlparser& 137 & $\frac{157}{741}$ & 21.19\%  & $\frac{131}{440}$ & 29.77\% \\[1ex]
rethinkdb\_rebirth &471 &  $\frac{545}{2246}$ & 24.27\% & $\frac{492}{2009}$ & 24.49\% \\[1ex]
xoreos & 732  & $\frac{2419}{3876}$  & 62.41\% & $\frac{2280}{3297}$ & 69.15\% \\[1ex]
libxmljs &630 &  $\frac{881}{3989}$ & 22.09\% & $\frac{790}{4008}$ & 19.71\% \\
tiny-differentiable &  \multirow{2}{*}{195} & \multirow{2}{*}{$\frac{747}{1282}$} & \multirow{2}{*}{58.27\%} & \multirow{2}{*}{$\frac{770}{1214}$} & \multirow{2}{*}{63.43\%} \\
-simulator          & & & & \\[1ex]
\midrule
\mc{6}{c}{\textbf{Overall}} \\
                   &    & \mc{1}{c}{Valid}  & \mc{1}{c}{Invalid} & \mc{1}{c}{\%} \\\midrule
 \multirow{3}{*}{Regex} & Mean & 890.67 &  \mc{1}{r}{1553.83} & 35.28\% \\
                       &  Med. & 671.00 & \mc{1}{r}{1579.00} & 23.88\%   \\
                       &  Std.Dev & 787.62 & \mc{1}{r}{956.31} & 19.48\%  \\\midrule
 \multirow{3}{*}{Comby} & Mean & 837.83 & \mc{1}{r}{1352.50} & 38.75\%  \\
                        &  Med. & 667.00 & \mc{1}{r}{1267.00} & 27.86\%  \\
                        &  Std.Dev & 745.78 & \mc{1}{r}{1058.33}& 21.66\%  \\\hline
\end{tabular}

@@

% ---------------- JAVA table UM Only--------------------------
\begin{table}[hbtp]
\centering
\caption{Java (Regex vs. Comby)}
\label{tab:table_java1}

\begin{tabular}{l|r|cr|cr}
\toprule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
pebble         & 279 & $\frac{86}{1014}$ & 8.48\% & $\frac{85}{752}$ & 11.30\%  \\[1ex]
spring-hateoas & 397 & $\frac{248}{2479}$ & 10.00\% & $\frac{172}{1384}$ & 12.43\%  \\[1ex]
javacc         & 363 & $\frac{542}{1888}$ & 28.70\% & $\frac{494}{1281}$ & 38.71\%  \\[1ex]
coffee-gb      & 463 & $\frac{224}{1927}$ & 11.63\% & $\frac{174}{798}$ & 21.80\% \\[1ex]
egads          & 252 & $\frac{624}{2427}$ & 25.43\% & $\frac{597}{1163}$ & 51.33\%  \\[1ex]
apk-parser     & 324 & $\frac{351}{1583}$ & 22.17\% & $\frac{333}{1199}$ & 27.77\%  \\[1ex]

% \multirow{6}{*}{Overall} & \multirow{3}{*}{Regex} & Mean & 345.83 & 1545.00  & 17.74\%& \\\cline{3-6}
%     &   &  Median & 299.50 & 1524.50 & 16.90\%  & \\\cline{3-6}
%     &   &  Std. Dev & 203.86 & 467.98 & 8.73\%  & \\\cline{2-6}

%  & \multirow{3}{*}{Comby} & Mean & 309.17 & 786.17 & 27.22\% & \\\cline{3-6}
%     &   &  Median & 253.50 & 724.50 & 24.79\%  & \\\cline{3-6}
%     &   &  Std. Dev & 202.44 & 235.24  & 15.59\%  & \\\hline

>>>>

\usepackage{code}
\usepackage{graphicx}
\usepackage{balance}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{listings}
\usepackage{booktabs}
%\usepackage{subfig}
\usepackage{float}
\usepackage{subcaption}
\usepackage{url}
\usepackage{comment}
\usepackage{xcolor}
\usepackage{xspace}

@@

% ---------------- C++ table UM Only--------------------------
\begin{table}[hbtp]
\centering
\caption{Regex vs. Comby for C++ (top) and Java (bottom)}
{\begin{subtable}[h]{\columnwidth}
%\caption{C++ (Regex vs. Comby)}
\label{tab:table_cpp1}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\[1ex]
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
ompl & 525 & $\frac{595}{2533}$ & 23.49\% &  $\frac{564}{2127}$  & 25.94\%   \\[1ex]
libgraphqlparser& 137 & $\frac{157}{741}$ & 21.19\%  & $\frac{131}{440}$ & 29.77\% \\[1ex]
rethinkdb\_rebirth &471 &  $\frac{545}{2246}$ & 24.27\% & $\frac{492}{2009}$ & 24.49\% \\[1ex]
xoreos & 732  & $\frac{2419}{3876}$  & 62.41\% & $\frac{2280}{3297}$ & 69.15\% \\[1ex]
libxmljs &630 &  $\frac{881}{3989}$ & 22.09\% & $\frac{790}{4008}$ & 19.71\% \\[1ex]
tiny-diff.-simulator &  195 & $\frac{747}{1282}$ &58.27\% &$\frac{770}{1214}$ & 63.43\% \\[1ex]
\bottomrule
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
                 & &       & Valid  & Invalid  & \% \\\midrule
\multirow{6}{*}{\textbf{Overall}} & \multirow{3}{*}{Regex} & Mean     & 890.67 &  1553.83 & 35.28\% \\
                         & & Med.    & 671.00 & 1579.00  & 23.88\%   \\
                         & & Std.Dev. & 787.62 & 956.31   & 19.48\%  \\\cline{2-6}
 & \multirow{3}{*}{Comby}  & Mean     & 837.83 & 1352.50 & 38.75\%  \\
                        & & Med.    & 667.00 & 1267.00 & 27.86\%  \\
                        & & Std.Dev. & 745.78 & 1058.33& 21.66\%  \\\bottomrule
\end{tabularx}
\end{subtable}}
\vspace{1ex}

{\begin{subtable}[h]{\columnwidth}
%\caption{Java }
\label{tab:table_java1}
\begin{tabularx}{\columnwidth}{X|r|cr|cr}
\toprule
                 &              & \multicolumn{2}{c|}{\textbf{Regex}} &\multicolumn{2}{c}{\textbf{Comby}}  \\
\textbf{Project} & \textbf{LOC} & $\frac{valid}{total}$ & \textbf{\%} & $\frac{valid}{total}$ &  \textbf{\%} \\[1ex]\midrule
pebble         & 279 & $\frac{86}{1014}$ & 8.48\% & $\frac{85}{752}$ & 11.30\%  \\[1ex]
spring-hateoas & 397 & $\frac{248}{2479}$ & 10.00\% & $\frac{172}{1384}$ & 12.43\%  \\[1ex]
javacc         & 363 & $\frac{542}{1888}$ & 28.70\% & $\frac{494}{1281}$ & 38.71\%  \\[1ex]
coffee-gb      & 463 & $\frac{224}{1927}$ & 11.63\% & $\frac{174}{798}$ & 21.80\% \\[1ex]
egads          & 252 & $\frac{624}{2427}$ & 25.43\% & $\frac{597}{1163}$ & 51.33\%  \\[1ex]
apk-parser     & 324 & $\frac{351}{1583}$ & 22.17\% & $\frac{333}{1199}$ & 27.77\%  \\[1ex]
\end{tabularx}
\begin{tabularx}{\columnwidth}{Xllrrr}
              & & & Valid  & Invalid  & \% \\\midrule
\multirow{6}{*}{\textbf{Overall}} & \mr{3}{Regex} & Mean     &  345.83 & 1545.00  & 17.74\% \\
              &   & Med.     & 299.50 & 1524.50 & 16.90\%  \\
              &   & Std.Dev. & 203.86 & 467.98 & 8.73\%  \\\cline{2-6}
& \mr{3}{Comby} & Mean     & 309.17 & 786.17 & 27.22\% \\
              &   & Med.     & 253.50 & 724.50 & 24.79\% \\
              &   & Std.Dev. & 202.44 & 235.24  & 15.59\% \\\bottomrule
\end{tabularx}
\end{subtable}}
\end{table}

@@

% ---------------- JAVA table UM Only--------------------------
\begin{table}[hbtp]
\centering
\end{table}
